### 2020-08-03 cases_and_policies/rmd/regressionsWithPlots.Rmd
update on DML

library(lfe)
library(stargazer)
library(knitr)
library(plm)
library(latex2exp)
library(ggplot2)
library(ggthemes)
library(estimatr)
library(gridExtra)
library(grid)
library(mvtnorm)
library(kableExtra)
library(data.table)
library(reshape2)

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
rootdir <- "/Users/Hiro/Documents/GitHub/covid-impact" 
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
```

@@

```{r corr, cache=FALSE}
cmat <-  cor(df[,c(bvars,pols)], use="pairwise.complete.obs")
scmat <-
  matrix(sprintf("%.2f",cmat),nrow=(length(bvars)+length(pols)))

@@

```{r casedieff, eval = FALSE, cache=FALSE, warning=FALSE, results='asis'}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

@@

L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdc"
for (k in 1:length(infovars)) { 
  # (1) policy index 
  pols <- c("pmaskbus","pk12","pindex") 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)  
  piy[[(1+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L) 
  # (2) excluding NY 
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(2+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) adding mask wearing rate  
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask"), c("z.mask"))
  piy[[(3+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote","party"), c("logvote","party"))
  piy[[(4+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(5+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (6) (2)-(5)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L) 
   sdf2 <- sdf[which(sdf$state!='New York'),]
  xlist <-list(c("z.mask","logvote","party"), c("z.mask","logvote","party"))
   piy[[(6+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
}

@@

  # (3) adding mask wearing rate 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask"), c("z.mask"))
  piy[[(3+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote"), c("logvote"))
  piy[[(4+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(5+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (6) (2)-(5)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
   # sdf2 <- sdf[which(sdf$state!='New York' & sdf$state!='New Jersey' & sdf$state!='Connecticut' & sdf$state!='Massachusetts'),]
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(6+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                xlist[[k]]),
              ilist[[k]], 0, L=L)

@@

    tbl <- capture.output(stargazer(
        lapply(piy, function(x) x$reg),
        type="latex",
        dep.var.labels.include=FALSE,
        title=ylbl,
        # omit=omit,
        # omit.labels=omit.labels,
        column.labels=c(yvar),
        column.separate=c(length(piy)),
        # add.lines=list(c("$\\sum_j \\mathrm{Policy}_j$",
        #                  sapply(piy, function(x) printstars(x$peff[1], x$peff[2]))),
        #                c("",
        #                  sprintf("(%.3f)",sapply(piy, function(x) x$peff[2])))
        #                ),
        omit.stat=c("f", "ser"), model.names=FALSE,
        no.space=TRUE,
        column.sep.width="1pt",
        df=FALSE, header=FALSE,
        model.numbers=TRUE))
    tbl <- relabel(tbl)
    tbl <- gsub("Model (\\d)", "\\(\\1\\)", tbl)
    #tbl <- gsub("No","Yes", tbl)
    texfile <- sprintf("%s/tex/tables_and_figures/%s-piy.tex",rootdir,prefix)
    cat(paste(tbl[c(-1,-2,-3,-4, -length(tbl))], collapse="\n"), file=texfile)

@@

colnames(piy[[1]]$reg$response) <- "dlogdd"  
showhtmltables(NULL, NULL,  piy);
#savetextables(NULL, NULL, piy[1:4], prefix="deaths-fe")

>>>>

library(lfe)
library(stargazer)
library(knitr)
library(plm)
library(latex2exp)
library(ggplot2)
library(ggthemes)
library(estimatr)
library(gridExtra)
library(grid)
library(mvtnorm)
library(kableExtra)
library(data.table)
library(reshape2)
library(AER)
library(hdm)
library(randomForest)

sgtype <- opts_knit$get("rmarkdown.pandoc.to")
sgstyle <- 'default'
colors <-  scale_color_solarized
colors_fill <- scale_fill_solarized
rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
rootdir <- "/Users/Hiro/Documents/GitHub/covid-impact" 
source(paste(rootdir,"cases_and_policies/R/exploratory.R", sep="/"))
source(paste(rootdir,"cases_and_policies/R/dataprep.R",sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/varlabels.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/regprep.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/generatetables.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/bootstrap_felm.R", sep="/"))
source(paste(rootdir,"cases_and_policies/rmd/rlassoPanel.R", sep="/"))
```

@@

```{r corr, cache=FALSE}

cmat <-  cor(df[,c(bvars,pols,"pindex")], use="pairwise.complete.obs")
scmat <-
  matrix(sprintf("%.2f",cmat),nrow=(length(bvars)+length(pols)+1))

@@

```{r casedieff, eval = TRUE, cache=FALSE, warning=FALSE, results='asis'}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

# L <- 14
#   xlist <- list("","")
#   plist <- list(pols, pols)
#   ijs <- expand.grid(1:length(bvars), 1:length(plist))
#   pib <- list()
#   for (k in 1:length(xlist)) {
#     pib[[k]] <- apply(ijs, 1, function(ij) {
#       policyreg(df, bvars[ij[1]], NULL,  bvars,
#                 c(plist[[ij[2]]],infovars[[k]],
#                   xlist[[k]]),
#                 ilist[[k]], "0", L=14)
#     })
#   }

@@

L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdc"
for (k in 1:length(infovars)) { 
  # (1) policy index 
  pols <- c("pmaskbus","pk12","pindex") 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)  
  piy[[(1+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L) 
  # (2) excluding NY 
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(2+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) adding mask wearing rate  
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("mask_percent"), c("mask_percent"))
  piy[[(3+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote"), c("logvote"))
  piy[[(4+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(5+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (6) (2)-(5)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L) 
   sdf2 <- sdf[which(sdf$state!='New York'),]
  xlist <-list(c("mask_percent","logvote"), c("mask_percent","logvote"))
   piy[[(6+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
}

@@

  # (3) adding mask wearing rate 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("mask_percent"), c("mask_percent"))
  piy[[(3+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) adding log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("logvote"), c("logvote"))
  piy[[(4+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (5) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(5+6*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (6) (2)-(5)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
   # sdf2 <- sdf[which(sdf$state!='New York' & sdf$state!='New Jersey' & sdf$state!='Connecticut' & sdf$state!='Massachusetts'),]
   sdf2 <- sdf[which(sdf$state!='New York'),]
  xlist <-list(c("mask_percent","logvote"), c("mask_percent","logvote"))
   piy[[(6+6*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                xlist[[k]]),
              ilist[[k]], 0, L=L)

@@

    tbl <- capture.output(stargazer(
        lapply(piy[1:4], function(x) x$reg),
        type="latex",
        dep.var.labels.include=FALSE,
        title=ylbl,
        # omit=omit,
        # omit.labels=omit.labels,
        column.labels=c(yvar),
        column.separate=c(length(piy[1:4])),
        # add.lines=list(c("$\\sum_j \\mathrm{Policy}_j$",
        #                  sapply(piy, function(x) printstars(x$peff[1], x$peff[2]))),
        #                c("",
        #                  sprintf("(%.3f)",sapply(piy, function(x) x$peff[2])))
        #                ),
        omit.stat=c("f", "ser"), model.names=FALSE,
        no.space=TRUE,
        column.sep.width="1pt",
        df=FALSE, header=FALSE,
        model.numbers=TRUE))
    tbl <- relabel(tbl)
    tbl <- gsub("Model (\\d)", "\\(\\1\\)", tbl)
    #tbl <- gsub("No","Yes", tbl)
    texfile <- sprintf("%s/tex/tables_and_figures/%s-piy.tex",rootdir,prefix)
    cat(paste(tbl[c(-1,-2,-3,-4, -length(tbl))], collapse="\n"), file=texfile)

@@

colnames(piy[[1]]$reg$response) <- "dlogdd"  
showhtmltables(NULL, NULL,  piy); 
prefix="deaths-fe"
#savetextables(NULL, NULL, piy[1:4], prefix="cases-fe")
   ylbl <- colnames(piy[[1]]$reg$response)
    if (ylbl=="dlogdd") ylbl <- "Death Growth"
    if (ylbl=="dlogdc") ylbl <- "Case Growth"

    tbl <- capture.output(stargazer(
        lapply(piy[1:4], function(x) x$reg),
        type="latex",
        dep.var.labels.include=FALSE,
        title=ylbl,
        # omit=omit,
        # omit.labels=omit.labels,
        column.labels=c(yvar),
        column.separate=c(length(piy[1:4])),
        # add.lines=list(c("$\\sum_j \\mathrm{Policy}_j$",
        #                  sapply(piy, function(x) printstars(x$peff[1], x$peff[2]))),
        #                c("",
        #                  sprintf("(%.3f)",sapply(piy, function(x) x$peff[2])))
        #                ),
        omit.stat=c("f", "ser"), model.names=FALSE,
        no.space=TRUE,
        column.sep.width="1pt",
        df=FALSE, header=FALSE,
        model.numbers=TRUE))
    tbl <- relabel(tbl)
    tbl <- gsub("Model (\\d)", "\\(\\1\\)", tbl)
    #tbl <- gsub("No","Yes", tbl)
    texfile <- sprintf("%s/tex/tables_and_figures/%s-piy.tex",rootdir,prefix)
    cat(paste(tbl[c(-1,-2,-3,-4, -length(tbl))], collapse="\n"), file=texfile)

## DML 
```{r regsdml, cache=FALSE, warning=FALSE, results='asis'}

library(glmnet)

df$logpop <- log(df$Population.2018)
df$logsq <- log(df$Square.Miles) 
df$repub <- as.factor(df$party)
df$party_dum <- ifelse(df$party == "republican", 0, 1) 
df$month3 <- ifelse(df$month==3,0,1)
df$month4 <- ifelse(df$month==4,0,1)
df$month5 <- ifelse(df$month==5,0,1)
df$month6 <- ifelse(df$month==6,0,1)
L <- 14
df$dlogdc.L14 <- panellag(df$dlogdc,df$state,df$date, lag=L)
df$logdc.L14 <- panellag(df$logdc,df$state,df$date, lag=L)
df$dlogdd.L14 <- panellag(df$dlogdd,df$state,df$date, lag=L)
df$logdd.L14 <- panellag(df$logdd,df$state,df$date, lag=L)  
df$pmaskbus.L14 <- panellag(df$pmaskbus,df$state,df$date, lag=L) 
df$pk12.L14 <- panellag(df$pk12,df$state,df$date, lag=L) 
df$pmovie.L14 <- panellag(df$pmovie,df$state,df$date, lag=L) 
df$pshelter.L14 <- panellag(df$pshelter,df$state,df$date, lag=L) 
df$prestaurant.L14 <- panellag(df$prestaurant,df$state,df$date, lag=L) 
df$pnonessential.L14 <- panellag(df$pnonessential,df$state,df$date, lag=L)  
df$pindex.L14 <- panellag(df$pindex,df$state,df$date, lag=L)

xvars <- c("logpop",
               "logsq",
               "Percent.Unemployed..2018.",
               "Percent.living.under.the.federal.poverty.line..2018.",
               "Percent.at.risk.for.serious.illness.due.to.COVID","party_dum",
               "mask_percent", "logvote",
               "month3","month4","month5","month6","dlogdc.L14","logdc.L14")

pols.L14 <- c("pmaskbus.L14","pk12.L14","pmovie.L14","pshelter.L14","prestaurant.L14","pnonessential.L14")

sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)

DML2.for.PLM <- function(x, d, y, dreg, yreg, sdf, nfold=5) {   
  unit <- as.double(sdf$state)
  j <-  quantile(unit, c(1:(nfold-1))/nfold)
  I <- vector(mode = "list", length = nfold)
  I[[1]] <- unit <= j[1] 
  for (b in 2:(nfold-1)) {
    I[[b]] <- (unit <= j[b])&(unit > j[b-1])
  } 
  I[[nfold]] <- unit > j[nfold-1]  
  nobs <- nrow(x)
  ytil <- dtil <- rep(NA, nobs)
  for(b in 1:nfold){
    I1 <- (I[[b]]==FALSE)
    I2 <- I[[b]]
    dfit <- dreg(x[I1,], d[I1]) # take a fold out
    yfit <- yreg(x[I1,], y[I1]) # take a folot out
    dhat <- predict(dfit, x[I2,], type="response") #predict the fold out
    yhat <- predict(yfit, x[I2,], type="response") #predict the fold out
    dtil[I2] <- (d[I2] - dhat) #record residual
    ytil[I2] <- (y[I2] - yhat) #record residual
    cat(b," ")
  }  
sdf$ytil <- ytil
sdf$dtil <- dtil 
rfit <- felm(ytil ~ dtil| 0| 0 | state, data=sdf) #estimate the main parameter by regressing one residual on the other
coef.est <- coef(rfit)[2] #extract coefficient 
se <- sqrt(vcov(rfit)[2,2]) 
cat(sprintf("\ncoef (se) = %g (%g)\n", coef.est , se))
return( list(coef.est = coef.est , se=se) )
}

# dreg <- function(x,d){ rlasso(x, d, c=2, POST=FALSE) } #ML method = rlasso
# yreg <- function(x,y){ rlasso(x, y, c=2, POST=FALSE) } #ML method = rlasso 
# DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf)

x = as.matrix(cbind(sdf[,pols.L14[-1]],sdf[,xvars]))
d = sdf$pmaskbus.L14
y = sdf$dlogdc

dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)

x = as.matrix(cbind(sdf[,pols.L14[-4]],sdf[,xvars]))
d = sdf$pshelter.L14
y = sdf$dlogdc

dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)

x = as.matrix(cbind(sdf[,pols.L14[1:2]],sdf[,xvars]))
d = sdf$pindex.L14
y = sdf$dlogdc

dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)

xvars <- c("logpop",
               "logsq",
               "Percent.Unemployed..2018.",
               "Percent.living.under.the.federal.poverty.line..2018.",
               "Percent.at.risk.for.serious.illness.due.to.COVID","party_dum",
               "mask_percent", "logvote",
               "month3","month4","month5","month6","dlogdd.L14","logdd.L14")

y = sdf$dlogdd  
dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)

x = as.matrix(cbind(sdf[,pols.L14[-4]],sdf[,xvars]))
d = sdf$pshelter.L14

dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)

x = as.matrix(cbind(sdf[,pols.L14[1:2]],sdf[,xvars]))
d = sdf$pindex.L14
y = sdf$dlogdd

dreg <- function(x,d){ cv.glmnet(x, d) } #ML method= rlasso
yreg <- function(x,y){ cv.glmnet(x, y) } #ML method = rlasso
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 5)
set.seed(1)
DML2.lasso <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold = 10)

dreg <- function(x,d){ randomForest(x, d) } #ML method=Forest
yreg <- function(x,y){ randomForest(x, y) } #ML method=Forest
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=5)
set.seed(1)
DML2.RF <- DML2.for.PLM(x, d, y, dreg, yreg, sdf, nfold=10)
